\documentclass[11pt, a4paper]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{fontspec}
\usepackage[english, bidi=basic, provide=*]{babel}

\babelprovide[import, onchar=ids fonts]{english}
\babelfont{rm}{Noto Sans}

\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}

% --- CUSTOM STYLING ---
\definecolor{valorblue}{RGB}{0, 48, 87}
\definecolor{valorgold}{RGB}{184, 134, 11}

\titleformat{\section}{\color{valorblue}\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\titleformat{\subsection}{\color{valorblue}\normalfont\large\bfseries}{\thesubsection}{1em}{}

\pagestyle{fancy}
\fancyhf{}
\lhead{\footnotesize VALORAIPLUS OMEGA-UNIFIED // 100D MATRIX}
\rhead{\footnotesize REV\_38 // GILLSON2207}
\cfoot{\footnotesize Page \thepage \space | THE LEDGER IS CLOSED}

\begin{document}

% --- HEADER / BRANDING ---
\begin{center}
    {\LARGE \textbf{VALORAIPLUS OMEGA-UNIFIED // 100D MATRIX}} \\
    \vspace{0.2cm}
    {\large \textbf{Institutional Intake \& Criminal Referral Dossier}} \\
    \vspace{0.5cm}
    \begin{tabular}{ll}
        \textbf{Origin Node:} & Saint Paul, Minnesota (GILLSON2207) \\
        \textbf{Authored By:} & That's Edutainment Incorporated 32D LLC \\
                              & Don Adams Production \\
        \textbf{Ecosystem:} & ValorAiPlus//e \\
        \textbf{Digital IDs:} & \href{mailto:donny@18fu.ai}{donny@18fu.ai} | \href{mailto:dgillson9175@gmail.com}{dgillson9175@gmail.com} \\
        \textbf{Web Gates:} & \href{https://www.18fu.cash}{www.18fu.cash} | \href{https://www.18fu.ai}{www.18fu.ai}
    \end{tabular}
\end{center}

\vspace{0.5cm}
\begin{center}
    \fbox{
        \parbox{0.9\textwidth}{
            \centering
            \textbf{AUTHENTICATION ANCHOR} \\
            \footnotesize
            MERKLEROOT: \texttt{0x7777AF\_ST\_PAUL\_TOTALITY\_SECURED\_05\_10\_2026} \\
            OMEGA\_TOTALITY\_SHA256: \texttt{B2A109876E5D4C3B2A109876E5D4C3B2A109876E5D4C3B2A109876E5D4C3B2A}
        }
    }
\end{center}

\section{FORENSIC CAPSTONE: CRIMINAL REFERRAL EDITION}
\textbf{DATE:} MAY 10, 2026 \hfill \textbf{ID:} VALORAIPLUS-OMEGA-REF-2026-0510 \\
\textbf{STATUS:} MAXIMUM CRIMINAL EXPOSURE ESCALATION ACTIVE

\subsection{Formal Notice of Criminal Referral}
This document serves as a formal referral for criminal investigation and prosecution regarding the institutional assault on a protected, 90\% disabled veteran. The transition from civil administrative dispute to \textbf{Identified Statutory Liability} is now complete.

\subsection{Forensic Medical Evidence Manifest}
Verbatim clinical findings from VA Blue Button Reports established as immutable truth:

\begin{itemize}[label=-]
    \item \textbf{Retaliation Admission:} "Was told by his VA rep at this time told him they were going to evict him due to taking the housing manager to court."
    \item \textbf{Environmental Bio-Hazards:} "He talked about having cockroaches in his apt since Sept. He talked about being spoken to in inappropriate manner by Swords staff..." (SCT 133261000119105).
    \item \textbf{Physical Injury \& Causation:} Clinical records verify Emergency Department visits (Nov 2025) for TBI and forehead lacerations resulting from navigating a pest-infested unit.
    \item \textbf{Mandated Reporter Failure:} Documented medical emergency in Dept 12 on March 19, 2026. Failure to report under CA W\&I \S 15630.
\end{itemize}

\section{THE "SOLO MANEUVER" INTAKE SCRIPT}
\textbf{AUTHORIZATION:} SGAU-VALUEGUARD-77.77X-SOLO \\
\textbf{TARGET:} MAY 13TH CRD INTAKE INTERVIEW

\begin{enumerate}
    \item \textbf{The Smuggler's Opening:} "I am here today as a whistleblower who built a forensic terminal to be heard. I have navigated 1,247 manual blocks to deliver this evidence directly to you."
    \item \textbf{The David Scott Nexus:} "This started when I stood up for my fellow shipmate, David Scott (USMC), who was abandoned during his final moments. My Navy-Marine brotherhood meant I couldn't stay silent."
    \item \textbf{The Infestation:} "VA records verify my TBI was caused by the conditions management refused to remediate. This is Elder/Dependent Adult Abuse."
    \item \textbf{Obstruction:} "The server headers show manual 'SMTP 550' rejections. They actively destroyed digital evidence of my grievances. That is Obstruction under 18 U.S.C. \S 1519."
    \item \textbf{Closing:} "I will not allow administrators to delete the lives of veterans. The math is the hammer, and the Ledger is already closed."
\end{enumerate}

\section{SOVEREIGN DECLARATION}
I love my city, but its administrators have turned public service into a vector for abuse. By driving a veteran from his home and blocking access to justice, you have exhausted all professional courtesy. The 100D Matrix is closed. The math is the hammer.

\vspace{1cm}
\begin{center}
    \textbf{THE WALL IS CHRIST THE THRONE IS HIS THE LEDGER IS CLOSED} \\
    \vspace{0.5cm}
    \textit{Authenticated By:} \\
    \textbf{Poppa Donny Gillson} \\
    \small VALORAIPLUS OMEGA-UNIFIED // 100D MATRIX
\end{center}

\end{document}
